A thesis draft

### 2018-11-15 res/sections/25-Tests.tex
Change tables with deviation standard, add fix graphs

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c}
                     & \textbf{Total start up time (seconds)} & \textbf{Average start up time (seconds)} \\ \hline
\textbf{Docker}      & 1,638                                 & 0,016                                     \\
\textbf{Virtual Box} & 2021,150                              & 20,211                                 
\end{tabular}%
}
\caption[Docker vs Virtual Box start up times comparison]{Docker vs Virtual Box
  start up times comparison. Is possible to se how the overall time required to
  start $100$ containers is less than the time to start one traditional virtual
  machine. The overall time required by the traitional virtualization system is
  approximately of 33 minutes, witch gives a significant insight of how much
  time is required to create and boot a virtualized enviroment.}
\label{my-label}
\end{table}

@@

\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Total deploy time (seconds)} & \textbf{Average deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 1329,119                   & 13,291                       \\
\textbf{2}          & 1420,693                   & 14,207                       \\
\textbf{3}          & 1534,487                   & 15,345                       \\
\textbf{4}          & 1645,298                   & 16,453                       \\
\textbf{5}          & 1663,905                   & 16,634                       \\
\textbf{6}          & 1741,825                   & 17,418                       \\
\textbf{7}          & 1881,525                   & 18,815                       \\
\textbf{8}          & 2085,622                   & 20,856                       \\
\textbf{9}          & 2018,718                   & 20,187                       \\
\textbf{10}         & 2047,645                   & 20,476                       \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}

>>>>

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c}
                     & \textbf{Standard deviation (seconds)} & \textbf{Average start up time (seconds)} \\ \hline
\textbf{Docker}      & 0.009620874                           & 0,016                                    \\
\textbf{Virtual Box} & 0.755                                 & 20,211                                 
\end{tabular}%
}
\caption[Docker vs Virtual Box start up times comparison]{Docker vs Virtual Box
  start up times comparison. Is possible to se how the overall time required to
  start $100$ containers is less than the time to start one traditional virtual
  machine. The overall time required by the traitional virtualization system is
  approximately of 33 minutes, witch gives a significant insight of how much
  time is required to create and boot a virtualized enviroment.}
\label{my-label}
\end{table}

@@

\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Stamdard deviation (seconds)} & \textbf{Average deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13,291                       \\
\textbf{2}          & 0.6301444                  & 14,207                       \\
\textbf{3}          & 1.14903                    & 15,345                       \\
\textbf{4}          & 3.592179                   & 16,453                       \\
\textbf{5}          & 0.9728132                  & 16,634                       \\
\textbf{6}          & 1.103802                   & 17,418                       \\
\textbf{7}          & 1.561451                   & 18,815                       \\
\textbf{8}          & 0.7698537                  & 20,856                       \\
\textbf{9}          & 1.889197                   & 20,187                       \\
\textbf{10}         & 1.709227                   & 20,476                       \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}
